---
title: "Economic factors of Great Recession"
output: flexdashboard::flex_dashboard
---
```{r Global Setup, include=FALSE, echo=FALSE, message=FALSE}

knitr::opts_chunk$set(fig.width = 5, fig.asp = 1/3)
```

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyr)
library(dplyr)
library(plotly)
library(ggplot2)
library(ggvis)
library(DT)
library(tidyverse)
library(lubridate)
library(Hmisc)
library(readr)
library(DT)
library(magrittr)
library(lubridate)
library(tidyverse)
library(RColorBrewer)
```
###                                   Report
```{r}
income<- read.csv('income.csv')
income <- na.omit(income)
```
Page 1
=====================================  
    
Column {data-width=600}
-------------------------------------
### ggplot of income- Data 2007
```{r}
aChart <- ggplot(income) +
    geom_col(aes(x = GeoName, y = X2007, fill=GeoName))+
    labs(title = "Income per state", 
         subtitle = "{in US $",
         caption = "Income",
         x= "State",
         y = "2007 Data(in $)",
         fill="GeoName")

plotly::ggplotly(aChart)

```




Column {data-width=400}
-------------------------------------
### ggplot income- 2008
```{r}
aChart <- ggplot(income) +
    geom_col(aes(x = GeoName, y = X2008, fill=GeoName))+
    labs(title = "Income per state", 
         subtitle = "{in US $",
         caption = "Income",
         x= "State",
         y = "2008 Data(in $)",
         fill="GeoName")

plotly::ggplotly(aChart)

```




### ggplot Income- 2009
```{r}
aChart <- ggplot(income) +
    geom_col(aes(x = GeoName, y = X2009, fill=GeoName))+
    labs(title = "Income per state", 
         subtitle = "{in US $",
         caption = "Income",
         x= "State",
         y = "2009 Data(in $)",
         fill="GeoName")

plotly::ggplotly(aChart)

```























Page 2 {data-orientation=rows}
=====================================     
   
Column {data-width=600}
-------------------------------------
```{r}
gdp<- read.csv('gdp.csv')
gdp <- na.omit(gdp)
```


### ggplot of GDP per state in 2008
```{r}
aChart <- ggplot(gdp) +
    geom_col(aes(x = GeoName, y = X2008, fill=GeoName))+
    labs(title = "GDP per state", 
         caption = "Gross domestic product",
         x= "State",
         y = "2008 Data($)",
         fill="GeoName")

plotly::ggplotly(aChart)


```



### Chart 2 ggplot of GDP per state in 2009
```{r}
aChart <- ggplot(gdp) +
    geom_col(aes(x = GeoName, y = X2009, fill=GeoName))+
    labs(title = "GDP per state", 
         caption = "Gross domestic product",
         x= "State",
         y = "2009 Data($)",
         fill="GeoName")

plotly::ggplotly(aChart)
```

Column {data-width=400}
-------------------------------------


### Chart 3 GDP per industry in different states in 2008
```{r}


p10 <- gdp %>% 
  group_by(GeoName) %>% 
  arrange(desc(GeoName)) %>% 
  head(100) %>% 
  select(X2008) %>% 
  DT::datatable(options = list(pageLength=500)) %>% 
  formatCurrency(columns = 'X2008') %>% 
  formatStyle(.,    'X2008',
    background = styleColorBar(gdp$X2008, 'steelblue'),
    backgroundSize = '100% 90%',
    backgroundRepeat = 'no-repeat',
    backgroundPosition = 'center'
  )
p10
```















Page 3
=====================================  
    
Column {data-width=600}
-------------------------------------


### ggplot of GDP per state in 2008
```{r}
aChart <- ggplot(gdp) +
    geom_col(aes(x = GeoName, y = X2008, fill=GeoName))+
    labs(title = "GDP per state", 
         caption = "Gross domestic product",
         x= "State",
         y = "2008 Data($)",
         fill="GeoName")

plotly::ggplotly(aChart)


```
   
Column {data-width=400}
-------------------------------------


### ggplot of GDP per state in 2009
```{r}
aChart <- ggplot(gdp) +
    geom_col(aes(x = GeoName, y = X2009, fill=GeoName))+
    labs(title = "GDP per state", 
         caption = "Gross domestic product",
         x= "State",
         y = "2009 Data($)",
         fill="GeoName")

plotly::ggplotly(aChart)
```



### GDP per industry in different states in 2008
```{r}


p10 <- gdp %>% 
  group_by(GeoName) %>% 
  arrange(desc(GeoName)) %>% 
  head(100) %>% 
  select(X2008) %>% 
  DT::datatable(options = list(pageLength=500)) %>% 
  formatCurrency(columns = 'X2008') %>% 
  formatStyle(.,    'X2008',
    background = styleColorBar(gdp$X2008, 'steelblue'),
    backgroundSize = '100% 90%',
    backgroundRepeat = 'no-repeat',
    backgroundPosition = 'center'
  )
p10
```














Page 4 {data-orientation=rows}
=====================================     
   
Column {data-width=600}
-------------------------------------


### Chart K

```{r}
p1 <- gdp %>%
  group_by(GeoName, Description = "Real GDP (millions of chained 2012 dollars)")%>%
  summarise(avg = mean(X2008))
  plot_ly(x = ~gdp$X2008,
          y = ~ gdp$GeoName,
          color = rainbow(48),
          type = 'bar')%>%
  layout(xaxis =list(title="Real GDP by State"),
         yaxis = list(title = "Count"))
p1

```

Column {data-width=400}
-------------------------------------


### Comparison of GDP between 2007 and 2008
```{r}

p4 <- plot_ly(gdp, x = ~X2007, na.rm = TRUE)%>%
  add_markers(y = ~ X2008,
              text = ~paste("X2008: ", X2008),
              showlegend = F)%>%
  add_lines (y = ~fitted(loess(X2008 ~ X2007), na.rm = TRUE),
             name = "Loess Smoother",
             color = I("#FFC125"),
             showlegend = T,
             line = list(width =5))%>%
  layout(xaxis = list(title = "X2007"),
         yaxis = list(title = "X2008"), na.rm = TRUE)

p4

```


###Comparison of GDP between 2008 and 2009

```{r}

p4 <- plot_ly(gdp, x = ~X2008, na.rm = TRUE)%>%
  add_markers(y = ~ X2009,
              text = ~paste("X2008: ", X2008),
              showlegend = F)%>%
  add_lines (y = ~fitted(loess(X2009 ~ X2008), na.rm = TRUE),
             name = "Loess Smoother",
             color = I("#FFC125"),
             showlegend = T,
             line = list(width =5))%>%
  layout(xaxis = list(title = "X2008"),
         yaxis = list(title = "X2009"), na.rm = TRUE)

p4

```








Page 5
=====================================  
    
Column {data-width=600}
-------------------------------------


### Box plots of gdp per State in 2007

```{r}

p6 <- gdp%>%
  group_by(GeoName)%>%
  ggvis(~GeoName, ~X2007, fill = ~GeoName)%>%
  layer_boxplots()
p6
```
   
Column {data-width=400}
-------------------------------------


###Boxplots of gdp per state in 2008
```{r}
p5<- gdp%>%
  group_by(GeoName)%>%
  ggvis(~GeoName, ~X2008, fill = ~GeoName)%>%
  layer_boxplots()
p5
```   


###Boxplots of gdp per state in 2009
```{r}
p5<- gdp%>%
  group_by(GeoName)%>%
  ggvis(~GeoName, ~X2009, fill = ~GeoName)%>%
  layer_boxplots()
p5
```








Page 6 {data-orientation=rows}
=====================================     
   
Column {data-width=600}
-------------------------------------
```{r}
wage<- read.csv('wages.csv')
wage <- na.omit(wage)
```


### ggplot of income- Data 2007
```{r}
aChart <- ggplot(wage) +
    geom_col(aes(x = GeoName, y = X2007, fill=GeoName))+
    labs(title = "Wage per state", 
         subtitle = "{in US $",
         caption = "Wage",
         x= "State",
         y = "2007 Data(in $)",
         fill="GeoName")

plotly::ggplotly(aChart)

```
Column {data-width=400}
-------------------------------------


### ggplot income- 2008
```{r}
aChart <- ggplot(wage) +
    geom_col(aes(x = GeoName, y = X2008, fill=GeoName))+
    labs(title = "Wage per state", 
         subtitle = "{in US $",
         caption = "Wage",
         x= "State",
         y = "2008 Data(in $)",
         fill="GeoName")
plotly::ggplotly(aChart)
```  


### ggplot Income- 2009
```{r}
aChart <- ggplot(wage) +
    geom_col(aes(x = GeoName, y = X2009, fill=GeoName))+
    labs(title = "Wage per state", 
         subtitle = "{in US $",
         caption = "Wage",
         x= "State",
         y = "2009 Data(in $)",
         fill="GeoName")

plotly::ggplotly(aChart)

```